### 2015-05-12 papers/histogram/thesis/poster.tex

\definecolor{bordercol}{RGB}{40,40,40}
\definecolor{headercol1}{RGB}{186,215,230}
\definecolor{headercol2}{RGB}{80,80,80}
\definecolor{headerfontcol}{RGB}{0,0,0}
\definecolor{boxcolor}{RGB}{186,215,230}

@@

\begin{poster}{
% options
    %% colors and appearance
    borderColor=bordercol, %
    headerColorOne=headercol1, %
    headerColorTwo=headercol2, %
    headerFontColor=headerfontcol, %
    boxColorOne=boxcolor, %
    textborder=rectangle, %
    headerborder=open, %
    background=none, %
    %% headers
    headerfont=\Large\sf\bf, %
    headerheight=0.11\textheight, %
    headershape=roundedright, %
    %% other
    columns=3 %
  }%
  {% top left logo
  }%
  {% title
    \LARGE\title
  }%
  {% authors
    \Large\author \\[1mm]
    \location
  }%
  {% top right logo
    % \includegraphics[width=2.5cm]{figs/osu.pdf}
    % \hspace{5mm}
  }%

@@

    \begin{itemize}
    \item Model systems are powerful tools for understanding complex
      physical systems, but they do not exist in the real world
    \item Direct experimental tests are not possible, so we test
      theories against Monte Carlo simulations instead
    \item Monte Carlo fluid simulations: moving spheres randomly to
      collect statistics on properties (e.g. internal energy, density,
      etc.) of valid fluid configurations
    \item Studying critical point requires sampling states with highly
      localized distribution of spheres, which is unlikely to occur by
      randomly sampling of all possible fluid configurations (second
      law of thermodynamics)
    \item For the square-well fluid, localized distribution of spheres
      is synonymous with a low energy state
    \end{itemize}

>>>>

\definecolor{border_color}{RGB}{40,40,40}
\definecolor{header_color_left}{RGB}{186,215,230}
\definecolor{header_color_right}{RGB}{80,80,80}
\definecolor{header_font_color}{RGB}{0,0,0}
\definecolor{box_color}{RGB}{186,215,230}

@@

\begin{poster}{
% options
    %% colors and appearance
    borderColor=border_color, %
    headerColorOne=header_color_left, %
    headerColorTwo=header_color_right, %
    headerFontColor=header_font_color, %
    boxColorOne=box_color, %
    textborder=rectangle, %
    headerborder=open, %
    background=none, %
    %% headers
    headerfont=\Large\sf\bf, %
    headerheight=0.11\textheight, %
    headershape=roundedright, %
    %% other
    columns=3 %
  }%
  {% top left logo
  }%
  {% title
    \LARGE\title
  }%
  {% authors
    \Large\author \\[1mm]
    \location
  }%
  {% top right logo
    % \includegraphics[width=2.5cm]{figs/osu.pdf}
    % \hspace{5mm}
  }%

@@

    \begin{itemize}
    \item Model systems are powerful tools for understanding complex
      physical systems, but they do not exist in the real world
    \item Theories tested against Monte Carlo simulations
    \item Monte Carlo fluid simulations: moving spheres randomly to
      collect statistics on properties (e.g. potential energy, density,
      etc.) of valid fluid configurations
    \item Studying critical point requires sampling states with highly
      localized distribution of spheres, which is unlikely to occur by
      randomly sampling of all possible fluid configurations (second
      law of thermodynamics)
    \item For the square-well fluid, localized distribution of spheres
      is synonymous with a low energy state
    \end{itemize}
